%-------------------------
% Resume in Latex
% Author : Sanchit Tanwar
% Adapted from: Amlaan Bhoi
% License : MIT
%------------------------

\documentclass[letterpaper,10.9pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex, hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{multicol}

\usepackage[charter]{mathdesign} % Bitstream Charter
% \usepackage{newpxtext,newpxmath} % Palatino

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.50in}
\addtolength{\evensidemargin}{-0.50in}
\addtolength{\textwidth}{1.0in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.5in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-5pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}
\newcommand{\resumeitem}[2]{
  \small{$\bullet$ #1}\hfill\raggedleft{$\bullet$ #2}
}
\newcommand{\resumeItemNoBullet}[2]{
  \item[]\small{
    \hspace{-9pt}\textbf{#1}{: #2 \vspace{-6pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item[]
  \begin{tabular*}{0.98\textwidth}{l@{\extracolsep{\fill}}r}
      \hspace{-10pt}\textbf{#1} & #2 \\
      \hspace{-10pt}\textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}
\newcommand{\resumesubheading}[4]{
  \vspace{-3pt}\item[]
  \begin{tabular*}{0.98\textwidth}{l@{\extracolsep{\fill}}r}
      \hspace{-10pt}\textbf{#1} & #2 \\
      \hspace{-10pt}\textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}
\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

% custom commands
\newcommand{\shorterSection}[1]{\vspace{-10pt}\section{#1}}
\newcommand{\shortersection}[2]{\vspace{11pt}\scshape\raggedright\large{\color{black}\titlerule \vspace{-10pt}#1}\hfill\scshape\large{#2}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------

\begin{center}
  \small \textbf{\huge Sanchit Tanwar} \\ 
  \vspace{5pt}
  \href{mailto:sanchittanwar75@gmail.com}{\color{blue}\underline{sanchittanwar75@gmail.com}} $\vert$
  {\color{blue}+919050402843} $\vert$
  LinkedIn: \href{https://www.linkedin.com/in/sanchit2843/}{\color{blue}\underline{sanchit2843}} $\vert$
  Github: \href{https://github.com/sanchit2843}{\color{blue}\underline{sanchit2843}} \\
\end{center}

 \shorterSection{Experience}
       
  \resumeSubHeadingListStart
  \vspace{-8pt}
    \resumeSubheading
      \small
      \item{\textbf{Computer Vision Research Intern}}{Attentive.ai (Jan 2020 - Present)}
      \vspace{-5pt}
            \item{
      Implementing Learning without forgetting and knowledge distillation for semantic segmentation applications. 
      % add the content of internship here
      }
        \vspace{-5pt}
     
      \item{
      Implementing and improving the performance of various Semantic segmentation model for Satellite and street imaging applications.
      % add the content of internship here
      }
                  \vspace{-5pt}
     
      \item{
      Change detection in buildings using aerial image dataset.
% add the content of internship here
      }
          \vspace{-5pt}
          
          \vspace{-8pt}
              \resumeSubheading
      \small
      \item{\textbf{Freelancing}}{freelancer.com (June 2019 - Present)}
      \vspace{-5pt}
      \item{
Detecting activities like sleeping and talking of students in a classroom, using face recognition and tracking for monthly feedback system for students, for an education startup.
      }
         \vspace{-5pt}
               \item{
Multi label human pose classification and joint angle prediction per frame trained on custom video dataset. 
      }
         \vspace{-5pt}
     
      \item{
 Calculating total footfall from video using CSRNet based crowd counting algorithms.
      }
      
          \vspace{-5pt}
       \item{
       Custom License Plate recognition and vehicle tracking software, implemented on Jetson Nano
}
          \vspace{-5pt}
          
          
  \resumeSubHeadingListEnd
%-----------EDUCATION-----------------
\shorterSection{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Thapar Institute of Engineering and Technology}{Patiala, India}
      {Bachelor of Engineering Electronics \& Communication;  CGPA: 8.4/10}{2016-2020}
      
      {
\begin{tabular}{p{12cm} p}
\small
$\bullet${ Machine learning} & 
\small
$\bullet$\hspace{2pt}Computer architecture\hfill \\
\small
$\bullet$ Image processing and computer vision& 
\small
$\bullet$\hspace{2pt}Embedded systems\hfill \\
\small
$\bullet$ Data structures and algorithms &
\small
 $\bullet$\hspace{2pt}Operating systems\hfill \\
\end{tabular}}
\vspace{-5pt}
    \resumeSubheading
      {DAV Public School}{Panipat, India}
      {High School;  Percentage: 90.2\%}{2015-2016}

  \resumeSubHeadingListEnd

%-----------SKILLS-----------------
\shorterSection{Skills}
  \resumeSubHeadingListStart
  \small
    \item{
     \textbf{Languages}{: Python, C++, Matlab}
    }
    \vspace{-5pt}
    \item{
    
    \textbf{Technologies}{: Deep Learning, Deep Reinforcement Learning(DQN, DDQN, A3C), Arduino, Raspberry pi, Latex}
    }
    \vspace{-5pt}
    \item{
     \textbf{Libraries}{: PyTorch, TensorFlow, Keras, Scikit-Learn, Numpy, Pandas, Jupyter, OpenCV, PIL, Librosa, NLTK}
    }
\resumeSubHeadingListEnd
%-----------PROJECTS-----------------
\shorterSection{Projects}
  \resumeSubHeadingListStart
  %Engagement 
    \resumeSubItem{Engagement Detection}
     {Research project under Dr. Vinay Kumar(DSP-IP lab) to detect engagement level of students.
        \vspace{-5pt}
        \begin{itemize}
            \item Developed a novel multi-modal attention guided CNN for user engagement recognition using Daisee dataset. 
        \end{itemize}
     }
           %Crime 
    \resumeSubItem{CrimeDetection}
      {Detecting crimes from CCTV footage using UCF crime dataset using MIL ranking algorithm and slow-fast networks for feature extraction. This project was done as a freelance work for a mexican company \href{http://www.redinmex.com/}{\color{blue}Redinmex}
      \href{mailto:ramswi@gmail.com}{ \color{blue}(contact)}}
      
     % Artificial eyes
    \resumeSubItem{\color{blue}\href{https://github.com/sanchit2843/ArtificialEyes}{Artificial Eyes}}{Device for blinds that uses CNN and LSTM to generate image captions(Show, attend and tell) and converts the captions to speech of desired language based on raspberry pi.}
    
    % Self driving car
    \resumeSubItem{\color{blue}\href{https://github.com/sanchit2843/SelfDrivingCar}{Self Driving Car}}
      {
      Self driving car using simulation tools.
        \vspace{-5pt}
        \begin{itemize}
            \item Lane finding in road images, traffic sign classifier.
            \item Steering angle prediction from driving video dataset.
            \item Vehicle detection and Segmentation using HRNet on Indian driving dataset. (Ongoing)
        \end{itemize}
      }
      

      %Healthcad
      
    \resumeSubItem{\color{blue}\href{https://github.com/sanchit2843/healthcad}{HealthCad}}
      {Implemented some of the latest deep learning algorithms to help doctors diagnose various diseases.
        \vspace{-5pt}
        \begin{itemize}
            \item Trained EfficientNet on malaria, chexpert, diabetic retinopathy dataset with class activation map generation to visualize results. 
            \item Conv-1d based neural network for atrial fibrillation classification using MIT-BIH dataset. 
        \end{itemize}
      }
      
      %GAN
      \resumeSubItem{\color{blue}\href{https://github.com/sanchit2843/GAN-applications}{GAN}}
      {Continuous project where I implement several applications of GAN's.
        \vspace{-5pt}
        \begin{itemize}
            \item Dog like image generation using DCGAN
            \item Semantic segmantation of city landscapes using pix2pix GAN.
        \end{itemize}
      }
      
      %RL
      \resumeSubItem{\color{blue}\href{https://github.com/sanchit2843/Reinforcementlearningprojects}{PongAI}}
      { Atari game (pong) playing AI based on DQN agent implemented using open ai gym and pytorch.
      }
  \resumeSubHeadingListEnd

%-----------Addtional information & Achievements-----------------
\shorterSection{Achievements}
  \resumeSubHeadingListStart
  \small
    \item{120k+ total views on several computer vision and deep learning blogs published on \color{blue}\href{https://medium.com/@sanchittanwar75}medium.}
    \vspace{-5pt}
    \item{Placed top 10 \% in 2 kaggle competetions of computer vision}
    \vspace{-5pt}
    \item{Received 5000\$ research credits from google cloud.}
    \vspace{-5pt}
    \item{Writer for Towards Data Science, The startup and Towards AI.}
    \vspace{-5pt}
  \resumeSubHeadingListEnd
  %-----------POR-----------------

  
%-----------interests------------------------

\shortersection{Interests}{additional information}

\vspace{6pt}
\begin{tabular}{p{11cm} p}
\small
$\bullet$ \color{blue}\href{https://medium.com/@sanchittanwar75}{Blogging} & 
\small
$\bullet$\hspace{2pt}A team player as well as an adept independent worker.\hfill \\
\small
$\bullet$ Music & 
\small
$\bullet$\hspace{2pt}Enthusiastic about improving my skills\hfill \\
\small
$\bullet$ Badminton & 
\small
 $\bullet$\hspace{2pt}Logical Approach\hfill
\end{tabular}
%-------------------------------------------
\end{document}
